\def\year{2020}\relax
%File: formatting-instruction.tex
\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage{aaai20}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet} % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{graphicx}  % DO NOT CHANGE THIS
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
%\nocopyright
%PDF Info Is REQUIRED.
% For /Author, add all authors within the parentheses, separated by commas. No accents or commands.
% For /Title, add Title in Mixed Case. No accents or commands. Retain the parentheses.
 \pdfinfo{
/Title (AAAI Press Formatting Instructions for Authors Using LaTeX -- A Guide)
/Author (AAAI Press Staff, Pater Patel Schneider, Sunil Issar, J. Scott Penberthy, George Ferguson, Hans Guesgen)
} %Leave this	
% /Title ()
% Put your actual complete title (no codes, scripts, shortcuts, or LaTeX commands) within the parentheses in mixed case
% Leave the space between \Title and the beginning parenthesis alone
% /Author ()
% Put your actual complete list of authors (no codes, scripts, shortcuts, or LaTeX commands) within the parentheses in mixed case. 
% Each author should be only by a comma. If the name contains accents, remove them. If there are any LaTeX commands, 
% remove them. 

% DISALLOWED PACKAGES
% \usepackage{authblk} -- This package is specifically forbidden
% \usepackage{balance} -- This package is specifically forbidden
% \usepackage{caption} -- This package is specifically forbidden
% \usepackage{color (if used in text)
% \usepackage{CJK} -- This package is specifically forbidden
% \usepackage{float} -- This package is specifically forbidden
% \usepackage{flushend} -- This package is specifically forbidden
% \usepackage{fontenc} -- This package is specifically forbidden
% \usepackage{fullpage} -- This package is specifically forbidden
% \usepackage{geometry} -- This package is specifically forbidden
% \usepackage{grffile} -- This package is specifically forbidden
% \usepackage{hyperref} -- This package is specifically forbidden
% \usepackage{navigator} -- This package is specifically forbidden
% (or any other package that embeds links such as navigator or hyperref)
% \indentfirst} -- This package is specifically forbidden
% \layout} -- This package is specifically forbidden
% \multicol} -- This package is specifically forbidden
% \nameref} -- This package is specifically forbidden
% \natbib} -- This package is specifically forbidden -- use the following workaround:
% \usepackage{savetrees} -- This package is specifically forbidden
% \usepackage{setspace} -- This package is specifically forbidden
% \usepackage{stfloats} -- This package is specifically forbidden
% \usepackage{tabu} -- This package is specifically forbidden
% \usepackage{titlesec} -- This package is specifically forbidden
% \usepackage{tocbibind} -- This package is specifically forbidden
% \usepackage{ulem} -- This package is specifically forbidden
% \usepackage{wrapfig} -- This package is specifically forbidden
% DISALLOWED COMMANDS
% \nocopyright -- Your paper will not be published if you use this command
% \addtolength -- This command may not be used
% \balance -- This command may not be used
% \baselinestretch -- Your paper will not be published if you use this command
% \clearpage -- No page breaks of any kind may be used for the final version of your paper
% \columnsep -- This command may not be used
% \newpage -- No page breaks of any kind may be used for the final version of your paper
% \pagebreak -- No page breaks of any kind may be used for the final version of your paperr
% \pagestyle -- This command may not be used
% \tiny -- This is not an acceptable font size.
% \vspace{- -- No negative value may be used in proximity of a caption, figure, table, section, subsection, subsubsection, or reference
% \vskip{- -- No negative value may be used to alter spacing above or below a caption, figure, table, section, subsection, subsubsection, or reference

\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.

% The file aaai20.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\setlength\titlebox{2.5in} % If your paper contains an overfull \vbox too high warning at the beginning of the document, use this
% command to correct it. You may not alter the value below 2.5 in
%\title{AAAI Press Formatting Instructions \\for Authors Using \LaTeX{} --- A Guide }
\title{ OD-LSTM: An Efficient Network For Named Entity Recognition }
%Your title must be in mixed case, not sentence case. 
% That means all verbs (including short verbs like be, is, using,and go), 
% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
% articles, conjunctions, and prepositions are lower case unless they
% directly follow a colon or long dash
%\author{Written by AAAI Press Staff\textsuperscript{\rm 1}\thanks{Primarily Mike Hamilton of the Live Oak Press, LLC, with help from the AAAI Publications Committee}\\ \Large \textbf{AAAI Style Contributions by
%Pater Patel Schneider,} \\ \Large \textbf{Sunil Issar, J. Scott Penberthy, George Ferguson, Hans Guesgen}\\ % All authors must be in the same font size and format. Use \Large and \textbf to achieve this result when breaking a line
%\textsuperscript{\rm 1}Association for the Advancement of Artificial Intelligence\\ %If you have multiple authors and multiple affiliations
% use superscripts in text and roman font to identify them. For example, Sunil Issar,\textsuperscript{\rm 2} J. Scott Penberthy\textsuperscript{\rm 3} George Ferguson,\textsuperscript{\rm 4} Hans Guesgen\textsuperscript{\rm 5}. Note that the comma should be placed BEFORE the superscript for optimum readability
%2275 East Bayshore Road, Suite 160\\
%Palo Alto, California 94303\\
%publications20@aaai.org % email address must be in roman text type, not monospace or sans serif
%}
\author{Junxiang Ge, Qi Zhang, Haizhou Zhao\\ 
AI Research Department, Sogou \\
Beijing, China}
 \begin{document}

\maketitle

\begin{abstract}
%AAAI creates proceedings, working notes, and technical reports directly from electronic source furnished by the authors. To ensure that all papers in the publication have a uniform appearance, authors must adhere to the following instructions. 
With the risen use of AI application, we need to understand some specific type of message from user's query. Named Entity Recognition(NER) is a basic task for that use. Gazzete is very useful when doing NER, howerver, most of the current method use iit in word embedding format, which will bring out the case, we need to retrain model when the word in gazzete is greatly changed. In this paper, we propose a conception, called Outer Dictionary(OD) LSTM, which means to use the outer type info of gazzete for each word, without using the specific word. Experiments shows it useful when doing NER task, and acheive a great improvement on task with which gazzete is heavily depended on.
\end{abstract}

%\noindent Congratulations on having a paper selected for inclusion in an AAAI Press proceedings or technical report! This document details the requirements necessary to get your accepted paper published using PDF\LaTeX{}. If you are using Microsoft Word, instructions are provided in a different document. AAAI Press does not support any other formatting software. 
%
%The instructions herein are provided as a general guide for experienced \LaTeX{} users. If you do not know how to use \LaTeX{}, please obtain assistance locally. AAAI cannot provide you with support and the accompanying style files are \textbf{not} guaranteed to work. If the results you obtain are not in accordance with the specifications you received, you must correct your source file to achieve the correct result. 
%
%These instructions are generic. Consequently, they do not include specific dates, page charges, and so forth. Please consult your specific written conference instructions for details regarding your submission. Please review the entire document for specific instructions that might apply to your particular situation. All authors must comply with the following:
%
%\begin{itemize}
%\item You must use the 2020 AAAI Press \LaTeX{} style file and the aaai.bst bibliography style file, which are located in the 2020 AAAI Author Kit (aaai20.sty and aaai.bst).
%\item You must complete, sign, and return by the deadline the AAAI copyright form (unless directed by AAAI Press to use the AAAI Distribution License instead).
%\item You must read and format your paper source and PDF according to the formatting instructions for authors.
%\item You must submit your electronic files and abstract using our electronic submission form \textbf{on time.}
%\item You must pay any required page or formatting charges to AAAI Press so that they are received by the deadline.
%\item You must check your paper before submitting it, ensuring that it compiles without error, and complies with the guidelines found in the AAAI Author Kit.
%\end{itemize}

\section{Introduction}

Named Entity Recognition (NER) is a base task when doing many language tasks. Usually, we need to extract mainly information from users' sentence to help us understand their meanings, and then use the extracted information to do further process. For example, in weather domain, we may need to extract \textbf{date and position} to help us understand when and where the user is asked towards the weather; in music type service, we may need to track \textbf{singer, song, style } entities to suit user's command; for many commom use, we need \textbf{person, location, organization} message to understand a sentence.

To accomplish this task, many method has been explored.  Convolution Neural Network (CNN) is used in Image Classification (Krizhevsky, Sutskever and Geoffrey 2012), and then proved also powerful in Text Classification (Kim 2014). CNN is also useful in NER tasks, whether to capture character-level features (;Ma and Hovy 2016), or to do word-level sequence labelling (Strubell et al. 2017).

\section{Related Work}

pass

\section{Outer Dictionary LSTM}

\subsection{Character-Base LSTM}
pass

\subsection{Tag Embedding Model}
pass

\section{Experiments}

pass

\section{Conclusion}

pass

\section{ Acknowledgments}
Especially grateful to Can Cui for denoting the music ner data, to Jindou Wu for advice on data processing of CCKS 2018 music dataset.

\section{References}

\smallskip \noindent
Krizhevsky, A.; Sutskever, I.; and Geoffrey E. H. 2012. ImageNet Classification with Deep Convolutional Neural Networks. In Proceedings of  Advances in Neural Information Processing Systems 25 (NIPS 2012).

\smallskip \noindent
Kim, Y. 2014. Convolutional Neural Networks for Sentence Classification. arXiv:1408.5882.

\smallskip \noindent
Sak, H.; Senior, A.; and Beaufays, F. 2014. Long Short-Term Memory Based Recurrent Neural Network Architectures for Large Vocabulary Speech Recognition. arXiv:1402.1128.

\smallskip \noindent 
Collobert, R.; Weston, J.; Bottou, L.; Karlen, M.; Kavukcuoglu, K.; and Kuksa, P. 2011. Natural Language Processing (Almost) from Scratch. Journal of Machine Learning Research 12 (2011) 2493-2537. 

\smallskip \noindent
Santos. C. N.; Xiang, B.; and Zhou, B. 2015. Classifying Relations by Ranking with Convolutional Neural Networks. arXiv:1504.06580. 

\smallskip \noindent
Strubell, E.; Verga, P.; Belanger, D.; and McCallum, A. 2017. Fast and Accurate Entity Recognition with Iterated Dilated Convolutions. arXiv:1702.02098. 

\smallskip \noindent
Peters, M. E.; Ammar, W.; Bhagavatula, C.; and Power. R.  2017. Semi-supervised sequence tagging with bidirectional language models. arXiv:1705.00108.

\smallskip \noindent 
Peters, M. E.; Neumann, M.; Iyyer, M.; Gardner, M.; Clark, C.; Lee, K.; and Zettlemoyer, L. 2018. Deep contextualized word representations. arXiv:1802.05365. 

\smallskip \noindent
Ma, X.; and Hovy, E. 2016. End-to-end Sequence Labeling via Bi-directional LSTM-CNNs-CRF. arXiv:1603.01354. 

\smallskip \noindent
Sang, E. F.; and Meulder, F. D. 2003. Introduction to the CoNLL-2003 Shared Task: Language-Independent Named Entity Recognition. arXiv:cs/0306050. 

\smallskip \noindent
Chiu, J. P.C.; and Nichols, E. 2016. Named Entity Recognition with Bidirectional LSTM-CNNs. Transactions of the Association for Computational Linguistics, Volume 4, 2016, p.357-370. 

\smallskip \noindent
Huang, Z.; Xu, W.; and Yu, K. 2015. Bidirectional LSTM-CRF Models for Sequence Tagging. arXiv:1508.01991. 

\smallskip \noindent
Vaswani, A.; Shazeer, N.; Parmar, N.; Uszkoreit, J.; Jones, L.; Gomez, A. N.; Kaiser, L.; and Polosukhin, I. 2017. Attention Is All You Need. arXiv:1706.03762. 

\smallskip \noindent
Peng, N.; and Dredze, M. 2016. Improving Named Entity Recognition for Chinese Social Media with Word Segmentation Representation Learning. arXiv:1603.00786. 

\smallskip \noindent
Chen, Q.; Zhuo, Z.; and Wang, W. 2019. BERT for Joint Intent Classification and Slot Filling. arXiv:1902.10909. 

\smallskip \noindent
Socher, R.; Manning, C. D.; and Andrew Y. Ng. 2010. Learning Continuous Phrase Representations and Syntactic Parsing with Recursive Neural Networks. In Proceedings of the NIPS-2010 Deep Learning and Unsupervised Feature Learning Workshop. 

\smallskip \noindent
Finkel, J. R.; Grenager, T.; and Manning, C. 2005. Incorporating non-local information into information extraction systems by Gibbs sampling. In Proceedings of the 43nd Annual Meeting of the Association for Computational Linguistics (ACL 2005), pp. 363-370. 

\smallskip \noindent
Peng, N.; and Dredze, M. 2015. Named Entity Recognition for Chinese Social Media with Jointly Trained Embeddings. In Proceedings of the 2015 Conference on Empirical Methods in Natural Language Processing (EMNLP). 

\smallskip \noindent
Mikolov, T.; Chen, K.; Corrado, G.; and Dean, J. 2013. Efficient Estimation of Word Representations in Vector Space. In Proceedings of Workshop at ICLR. 

\smallskip \noindent
Mikolov, T.; Sutskever, I.; Chen, K.; Corrado, G.; and Dean, J. 2013. Distributed Representations of Words and Phrases and their Compositionality. In Proceedings of NIPS. 

\smallskip \noindent
Mikolov, T.; Yih, W.; and Zweig, G. 2013. Linguistic Regularities in Continuous Space Word Representations. In Proceedings of NAACL HLT. 

\smallskip \noindent
Pennington, J.; Socher, R.; and Manning, C.D. 2014. GloVe: Global Vectors for Word Representation. In Proceedings of the 2014 Conference on Empirical Methods in Natural Language Processing (EMNLP), pages 1532–1543. 

\smallskip \noindent
Mikolov, T.; Grave, E.; Bojanowski, P.; Puhrsch, C.; and Joulin, A. 2017. Advances in Pre-Training Distributed Word Representations. arXiv:1712.09405. 

\end{document}
